---
title: 'R Environment'
date: "`r format(Sys.time())`"
fontfamily: mathpazo
fontsize: 11pt
output: html_document
author:
    - name: Dadong Zhang
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=TRUE, message=FALSE)

```

## basics

```{r}
library(rlang)
e1 <- env(
          a = FALSE,
          b = 'a',
          c = 2.3,
          d = 1:3
)
env_print(e1)
env_names(e1)
env_parent(e1)
env_parents(e1)

e1$a
e1[['c']]
# global_env() is also called workspace
identical(global_env(), current_env())
```
- Every name must be unique.

- The names in an environment are not ordered.

- An environment has a parent.

- Environments are not copied when modified.


## Special environments
- Each package attached by library() or require() becomes one of the parents of the global environment. The immediate parent of the global environment is the last package you attached31, the parent of that package is the second to last package you attached, …
```{r}
search()
search_envs()
base_env()
```
- A function binds the current environment when it is created. This is called the function environment, and is used for lexical scoping.
- Across computer languages, functions that capture (or enclose) their environments are called closures, which is why this term is often used interchangeably with function in R’s documentation.

```{r}

f <- function(x) x^2
fn_env(f)

```
- Namespaces: The goal of namespaces is to avoid conflict of loaded packages. Every function in a package is associated with a pair of environments: the package environment and the namespace environment.
- The package environment controls how we find the function; the namespace controls how the function finds its variables.
- Every binding in the package environment is also found in the namespace environment; this ensures every function can use every other function in the package. 

